Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-06-09 doc/manuscript/ESSDmanuscript.Rmd
rename file (disambiguation)

ForC_variables_included <- read.csv("figures_tables/ForC_variables_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
ForC_variables_included <- ForC_variables_included[c(1:5)] #include all fields but TO_DO

>>>>

ForC_variables_included <- read.csv("figures_tables/ForC_fields_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
ForC_variables_included <- ForC_variables_included[c(1:5)] #include all fields but TO_DO
